Pteropod physiological analysis

### 2018-07-31 figures.Rmd
removed 7b from figs

```{r effphy, fig.height = 5.33, fig.width = 12, eval = T}
toplo <- rbind(
    phymod[phymod$Model == 'mod8', ],
    phymod[phymod$Model == 'mod8', ],
    phymod[phymod$Model == 'mod10', ],
    phymod[phymod$Model == 'mod2', ]
  ) %>% 
  mutate(
    cvar = c('Temp', 'Ara', 'O2', 'Temp'),
    xvar = c('Omega[ar]', 'Temp', 'Temp','Omega[ar]'), 
    yvar = c('Dissolution', 'Dissolution', 'Dissolution', 'Abundance'), 
    legr = c('Temp', 'Omega[ar]', 'O[2]','Temp'),
    pos = c('right', 'left', 'left','left'), 
    fct = c(1.04, 0.97, 0.97, 0.92), 
    hjs = c(1, 0, 0, 0)
    ) %>% 
  mutate(
    pldat = pmap(list(Modobj, cvar, pos, fct), function(Modobj, cvar, pos, fct){

@@

p1 <- toplo$plos[[1]] + ggtitle('(a)')
p2 <- toplo$plos[[2]] + ggtitle('(b)')
p3 <- toplo$plos[[3]] + ggtitle('(c)')
p4 <- toplo$plos[[4]] + ggtitle('(d)')

pA <- ggplot_gtable(ggplot_build(p1))
pB <- ggplot_gtable(ggplot_build(p2))
pC <- ggplot_gtable(ggplot_build(p3))
pD <- ggplot_gtable(ggplot_build(p4))

maxWidth = grid::unit.pmax(pA$widths[2:3], pB$widths[2:3], pC$widths[2:3], pD$widths[2:3])

pA$widths[2:3] <- maxWidth
pB$widths[2:3] <- maxWidth
pC$widths[2:3] <- maxWidth
pD$widths[2:3] <- maxWidth

grid.arrange(
 pA, pB, pC, pD, ncol = 2 
)

```
Fig. 7 Examples of model interactions and additive effects of co-occurring environmental variables with biomineralization (shell dissolution) and population (abundance) responses. Co-occurring effects between aragonite saturation state (Ωar) and temperature on shell dissolution are shown in (a, b), temperature and O2 on dissolution in (c), and temperature and aragonite saturation state on abundance in (d). All y-axes are transformed to conform to model output. Covarying environmental variables were held constant at the minimum and maximum values in the observed data.

>>>>

```{r effphy, fig.height = 8, fig.width = 6, eval = T}
toplo <- rbind(
    phymod[phymod$Model == 'mod8', ],
    phymod[phymod$Model == 'mod10', ],
    phymod[phymod$Model == 'mod2', ]
  ) %>% 
  mutate(
    cvar = c('Temp', 'O2', 'Temp'),
    xvar = c('Omega[ar]', 'Temp','Omega[ar]'), 
    yvar = c('Dissolution', 'Dissolution', 'Abundance'), 
    legr = c('Temp', 'O[2]','Temp'),
    pos = c('right', 'left','left'), 
    fct = c(1.04, 0.97, 0.92), 
    hjs = c(1, 0, 0)
    ) %>% 
  mutate(
    pldat = pmap(list(Modobj, cvar, pos, fct), function(Modobj, cvar, pos, fct){

@@

p1 <- toplo$plos[[1]] + ggtitle('(a)')
p2 <- toplo$plos[[2]] + ggtitle('(b)')
p3 <- toplo$plos[[3]] + ggtitle('(c)')

grid.arrange(
 pA, pB, pC, ncol = 1 
)

```
Fig. 7 Examples of model interactions and additive effects of co-occurring environmental variables with biomineralization (shell dissolution) and population (abundance) responses. Co-occurring effects between aragonite saturation state (Ωar) and temperature on shell dissolution are shown in (a), temperature and O2 on dissolution in (b), and temperature and aragonite saturation state on abundance in (c). All y-axes are transformed to conform to model output. Covarying environmental variables were held constant at the minimum and maximum values in the observed data.
